CodeBook
===========

File to explain project feature (or, variable) names and data processing steps

```Shell
Author: Elliot Kleiman
File..: CodeBook.Rmd
Desc..: File to explain work involved in cleaning up feature names reducing data dimensionality
Date..: Sat Nov 22 20:54:55 EST 2014
```

```{r loadFeatureData, echo = FALSE}
load(file = "./data/mean.std.features.rda")
load(file = "./data/mean.features.clean.rda")
load(file = "./data/std.features.clean.rda")
```

##### Data transformations

The data set was reduced in dimensionality from
measuring 561 features over 10299 observations to 
measuring 66 features over 180 aggregated observations.

The final tidy data set consists of 66 features grouped 
first by activity then by subject. For each feature, the 
mean was computed over each activity-subject combination.

##### Feature (or, variable) name transformation and selection

The feature names were transformed (or, cleaned) as follows:

All parenthesis `()`, and `-`, characters in the feature names were
removed by whitespace and the `.` character respectively. Duplicate
feature names, such as `BodyBody` were deduplicated to `Body` to display
only a single value.

Feature names were selected based on grepping for the substring `mean()` or `std()`.
All other feature names were omitted. This reduced the dimensionality of the
features under study from 561 to 66.

##### Feature abbreviation key:

```Shell
t       = Time
f       = Frequency, obtained by Fast Fourier Transform
X       = X dimensional axis
Y       = Y dimensional axis
Z       = Z dimensional axis
Acc     = Acceleration
Mag     = Magnitude
std     = Standard deviation
Body    = Human body of subject
Gyro    = Gyroscope
Jerk    = Jerk signal
mean    = Mean value
Gravity = Gravity acceleration
```

For a listing of all transformed and selected feature names as they appear 
in file `tidy.txt` see following section `Feature names and their descriptions`.

##### Feature names and their descriptions:

```{r displayFeatureData, echo = FALSE}
description <- c(
"mean of body linear acceleration measured on X-axis",
"mean of body linear acceleration measured on Y-axis",
"mean of body linear acceleration measured on Z-axis",
"mean of gravity acceleration measured on X-axis",
"mean of gravity acceleration measured on Y-axis",
"mean of gravity acceleration measured on Z-axis",
"mean of body linear acceleration with jerk signal measured on X-axis",
"mean of body linear acceleration with jerk signal measured on Y-axis",
"mean of body linear acceleration with jerk signal measured on Z-axis",
"mean of body gyroscope measured on X-axis",
"mean of body gyroscope measured on Y-axis",
"mean of body gyroscope measured on Z-axis",
"mean of body gyroscope with jerk signal measured on X-axis",
"mean of body gyroscope with jerk signal measured on Y-axis",
"mean of body gyroscope with jerk signal measured on Z-axis",
"mean of body linear acceleration magnitude",
"mean of gravity acceleration magnitude",
"mean of body linear acceleration with jerk magnitude",
"mean of body gyroscope magnitude",
"mean of body gyroscope with jerk signal magnitude",
"mean of frequency body linear acceleration measured on X-axis",
"mean of frequency body linear acceleration measured on Y-axis",
"mean of frequency body linear acceleration measured on Z-axis",
"mean of frequency body linear acceleration with jerk signal measured on X-axis",
"mean of frequency body linear acceleration with jerk signal measured on Y-axis",
"mean of frequency body linear acceleration with jerk signal measured on Z-axis",
"mean of frequency body gyroscope measured on X-axis",
"mean of frequency body gyroscope measured on Y-axis",
"mean of frequency body gyroscope measured on Z-axis",
"mean of frequency body linear acceleration magnitude",
"mean of frequency body linear acceleration with jerk signal magnitude",
"mean of frequency body gyroscope magnitude",
"mean of frequency body gyroscope with jerk signal magnitude",
"std of body linear acceleration measured on X-axis",
"std of body linear acceleration measured on Y-axis",
"std of body linear acceleration measured on Z-axis",
"std of gravity acceleration measured on X-axis",
"std of gravity acceleration measured on Y-axis",
"std of gravity acceleration measured on Z-axis",
"std of body linear acceleration with jerk signal measured on X-axis",
"std of body linear acceleration with jerk signal measured on Y-axis",
"std of body linear acceleration with jerk signal measured on Z-axis",
"std of body gyroscope measured on X-axis",
"std of body gyroscope measured on Y-axis",
"std of body gyroscope measured on Z-axis",
"std of body gyroscope with jerk signal measured on X-axis",
"std of body gyroscope with jerk signal measured on Y-axis",
"std of body gyroscope with jerk signal measured on Z-axis",
"std of body linear acceleration magnitude",
"std of gravity acceleration magnitude",
"std of body linear acceleration with jerk magnitude",
"std of body gyroscope magnitude",
"std of body gyroscope with jerk signal magnitude",
"std of frequency body linear acceleration measured on X-axis",
"std of frequency body linear acceleration measured on Y-axis",
"std of frequency body linear acceleration measured on Z-axis",
"std of frequency body linear acceleration with jerk signal measured on X-axis",
"std of frequency body linear acceleration with jerk signal measured on Y-axis",
"std of frequency body linear acceleration with jerk signal measured on Z-axis",
"std of frequency body gyroscope measured on X-axis",
"std of frequency body gyroscope measured on Y-axis",
"std of frequency body gyroscope measured on Z-axis",
"std of frequency body linear acceleration magnitude",
"std of frequency body linear acceleration with jerk signal magnitude",
"std of frequency body gyroscope magnitude",
"std of frequency body gyroscope with jerk signal magnitude",
"subject",
"activity")

# Write feature names and their descriptions
data.frame(feature.name = mean.std.features, feature.description = description)
```